% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[preprint]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{amsfonts}
\usepackage{array} % for p{} column type
\usepackage{graphicx} % for \resizebox
\usepackage{makecell}
% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{enumitem}
\newcommand{\ie}{\emph{i.e., }}
\newcommand{\eg}{\emph{e.g., }}
\newcommand{\etal}{\emph{et al. }}
\newcommand{\st}{\emph{s.t. }}
\newcommand{\etc}{\emph{etc.}}
\newcommand{\wrt}{\emph{w.r.t. }}
\newcommand{\cf}{\emph{cf. }}
\newcommand{\aka}{\emph{a.k.a. }}
\newcommand{\edit}[1]{\textcolor{blue}{#1}}
\newcommand{\fb}{\textcolor{blue}}
\newcommand{\mx}{\textcolor{red}}


\title{Dual-Phase Accelerated Prompt Optimization}


\author{
Muchen Yang\textsuperscript{1}, 
~Moxin Li\textsuperscript{2}\thanks{\hspace{2mm}Corresponding Author},
~Yongle Li\textsuperscript{3}, 
~Zijun Chen\textsuperscript{3}, \\
\textbf{
~Chongming Gao\textsuperscript{1}\footnotemark[1],
~Junqi Zhang\textsuperscript{4},
~Yangyang Li\textsuperscript{5},
~Fuli Feng \textsuperscript{1,3}
}
\\
\textsuperscript{1}University of Science and Technology of China, 
~\textsuperscript{2}National University of Singapore\\
\textsuperscript{3}Institute of Dataspace, Hefei Comprehensive National Science Center \\
~\textsuperscript{4}AtomEcho Inc.,
~\textsuperscript{5}Academy of Cyber
\\
\tt{muchen00@mail.ustc.edu.cn},
\tt{limoxin@u.nus.edu},
~\tt{liyongle999@gmail.com}\\
~\tt{zijunchen248@gmail.com},
\tt{chongminggao@ustc.edu.cn},
~\tt{zhangjunqi@atomecho.xyz}\\ 
~\tt{liyangyang@live.com},
~\tt{fulifeng93@gmail.com}\\
}

\begin{document}
\maketitle


\begin{abstract}
Gradient-free prompt optimization methods have made significant strides in enhancing the performance of closed-source Large Language Models (LLMs) across a wide range of tasks. 
However, existing approaches make light of the importance of high-quality prompt initialization and the identification of effective optimization directions, thus resulting in substantial optimization steps to obtain satisfactory performance.
In this light, we aim to accelerate prompt optimization process to tackle the challenge of low convergence rate. 
We propose a dual-phase approach which starts with generating high-quality initial prompts by adopting a well-designed meta-instruction to delve into task-specific information, and iteratively optimize the prompts at the sentence level, leveraging previous tuning experience to expand prompt candidates and accept effective ones.
Extensive experiments on eight datasets demonstrate the effectiveness of our proposed method, achieving a consistent accuracy gain over baselines with less than five optimization steps. 

\end{abstract}

\input{1_introduction_0614}
\input{2_related_work}
\input{3_method}
\input{4_experiments}
\input{5_conclusion}
\input{7_Acknowledgement}

\clearpage
\newpage
\input{6_limitation}

\bibliography{custom}

\end{document}
